### 2012-06-13 inst/examples/cost_of_bias.Rmd
cost of bias, zero

```{r}
#require(snowfall)
#sfInit(parallel=T, cpu=16)
#sfLibrary(pdgControl)
#sfExportAll()
set.seed(42)
sims_four <- lapply(1:100, function(i){
  est_pars[1] <- bias[i] 
  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, det_opt$D, z_g, z_m, z_i, profit)
})
````

>>>>

```{r}
#require(snowfall)
#sfInit(parallel=T, cpu=16)
#sfLibrary(pdgControl)
#sfExportAll()
set.seed(42)
sims_four <- lapply(1:100, function(i){
  est_pars[1] <- bias[i] 
  SDP_Mat <- determine_SDP_matrix(f, est_pars, x_grid, h_grid, sigma_g )
  opt <- find_dp_optim(SDP_Mat, x_grid, h_grid, OptTime=25, xT=0, 
                     profit, delta=0.05, reward=0)
  ForwardSimulate(f, est_pars, x_grid, h_grid, x0=K, opt$D, z_g, z_m, z_i, profit)
})
````
